Killer Plot

### 2023-04-16 killer_plot1.Rmd

```{r slay, echo=FALSE, results='hide'}
bar_run <- function(plot_race,plot_year){
  new_df <- citations_htx_bar[which(citations_htx_bar$date == plot_year), ]
  new_df <- new_df[which(citations_htx_bar$subject_race == plot_race),]
  male_df <- new_df[which(new_df$subject_sex == "male"),]
  female_df <- new_df[which(new_df$subject_sex == "female"),]
  red_stop_m <- sum(male_df$red_stop == 1)
  red_stop_f <- sum(female_df$red_stop == 1)
  seat_belt_m <- sum(male_df$seat_belt == 1)
  seat_belt_f <- sum(female_df$seat_belt == 1)
  fin_resp_m <- sum(male_df$fin_resp == 1)
  fin_resp_f <- sum(female_df$fin_resp == 1)
  license_m <- sum(male_df$license == 1)
  license_f <- sum(female_df$license == 1)
  speeding_m <- sum(male_df$speeding == 1)
  speeding_f <- sum(female_df$speeding == 1)
  barplot(red_stop_m, red_stop_f, seat_belt_m, seat_belt_f, fin_resp_m, fin_resp_f, license_m, license_f, speeding_m, speeding_f)
}
#bar_run("white", 2014)  
```

>>>>

```{r slay, echo=FALSE, results='hide'}
bar_run <- function(plot_race,plot_year){
  new_df <- citations_htx_bar[which(citations_htx_bar$date == plot_year &
                                      citations_htx_bar$subject_race==plot_race), ]
  male_df <- new_df[which(new_df$subject_sex == "male"),]
  female_df <- new_df[which(new_df$subject_sex == "female"),]
  red_stop_m <- sum(male_df$red_stop == 1)
  red_stop_f <- sum(female_df$red_stop == 1)
  seat_belt_m <- sum(male_df$seat_belt == 1)
  seat_belt_f <- sum(female_df$seat_belt == 1)
  fin_resp_m <- sum(male_df$fin_resp == 1)
  fin_resp_f <- sum(female_df$fin_resp == 1)
  license_m <- sum(male_df$license == 1)
  license_f <- sum(female_df$license == 1)
  speeding_m <- sum(male_df$speeding == 1)
  speeding_f <- sum(female_df$speeding == 1)
  barplot(red_stop_m, red_stop_f, seat_belt_m, seat_belt_f, fin_resp_m, fin_resp_f, license_m, license_f, speeding_m, speeding_f)
}
#bar_run("white", 2014)  
```
